API design for machine learning software: experiences from the scikit-learn project

### 2013-06-27 paper.tex
Cosmit.

In most machine learning tasks, data is modeled as a set of variables.  For
example, in a classification or regression task, the goal is to find a mapping
between input variables $X_1, ..., X_p$, called features, and
some output variable $Y$. A sample is then defined as a tuple of values $([x_1,
..., x_p]^\mathrm{T}, y)$ of these variables and a dataset as a collection of
such samples.  As such, matrices of numerical values constitute a natural and
a widely used representation in machine learning: each row in the
matrix corresponds to one sample of the dataset and each column to one
variable of the problem.

>>>>

In most machine learning tasks, data is modeled as a set of variables.  For
example, in a classification or regression task, the goal is to find a mapping
between input variables $X_1, ..., X_p$, called features, and
some output variable $Y$. A sample is then defined as a tuple of values $([x_1,
..., x_p]^\mathrm{T}, y)$ of these variables and a dataset as a collection of
such samples.  As such, matrices of numerical values constitute a natural and
widely used representation in machine learning: each row in the
matrix corresponds to one sample of the dataset and each column to one
variable of the problem.
